### 2011-02-04 paper/introduction.tex
More edits to intro, hyperNeatMethod

Gaits for walking robots are often designed with some explicit or
implicit goal in mind.  For some applications, the design criteria may
be obvious: perhaps the robot needs to move as quickly or as
efficiently as possible, or with minimal power usage or strain on
actuators.  In many cases, however, the objective is more complicated,
requiring simultaneous optimization of several desired traits, each
with its own relative importance.  For example, Honda's Asimo
\cite{_asmio} and Boston Dynamic's Big Dog \cite{_bigdog} both require
gaits that are relatively quick, power efficient, and robust to
changing terrain, but with they vary widely in the importance placed
on each attribute.  A primary concern for Big Dog's gait is that it is
robust to steep terrain, whereas

>>>>

Gaits for walking robots are often designed with some explicit or
implicit goal in mind.  For some applications, the design criteria may
be obvious --- perhaps the robot needs to move as quickly or as
efficiently as possible --- but other times the objective is more complicated,
requiring simultaneous optimization of several desired traits, each
with its own relative importance.  The different combinations of desired traits and the relative weight placed on each can produce drastically different gaits.    For example, Honda's Asimo
\cite{_asmio} and Boston Dynamic's Big Dog \cite{_bigdog} both require
gaits that are relatively quick, power efficient, and robust to
changing terrain, but they vary widely in the importance placed
on each attribute.  Big Dog's gait is optimzed for much more difficult terrain than Asimo's, resulting in a gait of a completely different form.

Whatever the design goals, gaits may be obtained by one of several methods.  Gaits may be designed by hand by an expert, as in \cite{_asmio, _bigdog}, or they may be learned by repeated trial and evaluation.  Learned gaits offer several advantages over manually designed gaits.  Automatically learning gaits can save valuable engineering time and can allow customization of gaits to a particular robot and its unique actuators.  Most importantly, learned gaits can outperform manually designed gaits

save programmer time
customize gaits per model
design better gaits than people

In many cases additional objectives may be

, or with minimal power usage or strain on
actuators.  In many cases, however,
